Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-04 journal paper/content/sec-theory.tex
In theory/extensions, added xhdrs re beliefs and non-stationary response function.

>>>>

\asedit{\xhdr{Beliefs.} Rather than knowing the principals' algorithms $(\alg[1],\alg[2])$, the Bayesian prior $\priorMu$, and the response function $\respF$, agents could have beliefs on these objects that need not be correct. If agents have common ``point beliefs", respectively, algorithms $(\alg[1]',\alg[2]')$ prior $\priorMu'$ and response function $\respF'$,  then all our results carry over with respect to these beliefs.}

\asedit{\xhdr{Limited non-stationarity in $\respF$.} 
Different agents can have different response functions, in the following sense. For \HardMaxRandom, our results carry over if each agent $t$ has a \HardMaxRandom response function $\respF$ with parameter $\eps_t\geq \eps_0$. For \SoftMaxRandom, different agents can have different response functions that satisfy Definition~\ref{def:SoftMax} (with the same parameters).}
